Three 38 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-02-28 papers/authors.tex
stage Cep-Her outline

\author[0000-0002-0514-5538]{L. G. Bouma}
\altaffiliation{51 Pegasi b Fellow}
\affiliation{Cahill Center for Astrophysics, California Institute of Technology, Pasadena, CA 91125, USA}
\affiliation{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08540, USA}

% Key authors:
% ... stellar rotation & the initial crossmatch
\author[0000-0002-2792-134X]{J. L. Curtis}
\affiliation{Department of Astronomy, Columbia University, 550 West 120th Street, New York, NY 10027, USA}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY 10024, USA}

% ... Kepler correlations
\author[0000-0003-1298-9699]{K. Masuda}
\affiliation{Department of Earth and Space Science, Osaka University, Osaka 560-0043, Japan}

% ... HIRES PI
\author{L. A. Hillenbrand}
\affiliation{Cahill Center for Astrophysics, California Institute of Technology, Pasadena, CA 91125, USA}
% pending

% ... RM fitting
\author[0000-0001-7409-5688]{G. Stefansson}
\altaffiliation{Henry Norris Russell Fellow}
\affiliation{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08540, USA}

%
% PFS Collaborators
%
% \author[0000-0001-8638-0320]{A. W. Howard} % preferred acknowledgements
% \affiliation{Cahill Center for Astrophysics, California Institute of Technology, Pasadena, CA 91125, USA}
%
\author[0000-0002-0531-1073]{H. Isaacson}
\affiliation{Astronomy Department, University of California, Berkeley, CA 94720, USA}
% pending

%
% MUSCAT3 Collaborators
%
\author[0000-0001-8511-2981]{N. Narita}
\affiliation{Komaba Institute for Science, The University of Tokyo, Tokyo 153-8902, Japan}
\affiliation{Japan Science and Technology Agency, PRESTO, Tokyo 153-8902, Japan}
\affiliation{Astrobiology Center, Tokyo 181-8588, Japan}
\affiliation{Instituto de Astrof\'{i}sica de Canarias (IAC), 38205 La Laguna, Tenerife, Spain}

\author[0000-0002-4909-5763]{A. Fukui} % afukui@g.ecc.u-tokyo.ac.jp
\affiliation{Komaba Institute for Science, The University of Tokyo, Tokyo 153-8902, Japan}
\affiliation{Instituto de Astrof\'{i}sica de Canarias (IAC), 38205 La Laguna, Tenerife, Spain}

\author[0000-0002-5658-5971]{M. Ikoma} % ikoma.masahiro@gmail.com
\affiliation{Division of Science, National Astronomical Observatory of Japan, Tokyo 181-8588, Japan}

\author[0000-0002-6510-0681]{M. Tamura} % motohide.tamura@nao.ac.jp
\affiliation{Department of Astronomy, The University of Tokyo, Tokyo 113-0033, Japan}
\affiliation{Astrobiology Center, Tokyo 181-8588, Japan}
\affiliation{Division of Science, National Astronomical Observatory of Japan, Tokyo 181-8588, Japan}

% AO IMAGING
\author[0000-0001-9811-568X]{A.~L.~Kraus}
\affiliation{Department of Astronomy, The University of Texas at Austin, Austin, TX 78712, USA}

\author[0000-0001-9800-6248]{E. Furlan} % furlan@ipac.caltech.edu
\affiliation{NASA Exoplanet Science Institute, Caltech/IPAC, Pasadena, CA 91125, USA}

\author[0000-0003-2519-6161]{C.~L.~Gnilka} % clgnilka@gmail.com
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}
\affiliation{NASA Exoplanet Science Institute, Caltech/IPAC, Pasadena, CA 91125, USA}

\author[0000-0002-9903-9911]{K.~V.~Lester} % klester192@gmail.com
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}
% pending

\author[0000-0002-2532-2853]{S. B. Howell}
\affiliation{NASA Ames Research Center, Moffett Field, CA 94035, USA}

>>>>

\author[0000-0002-0514-5538]{L. G. Bouma}
\altaffiliation{51 Pegasi b Fellow}
\affiliation{Cahill Center for Astrophysics, California Institute of Technology, Pasadena, CA 91125, USA}
%\affiliation{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08540, USA}

% Key authors:
% ... Kinematics
\author[0000-0002-6549-9792]{R.~Kerr}
\affiliation{Department of Astronomy, The University of Texas at Austin, Austin, TX 78712, USA}% % ... Kepler correlations

% ... stellar rotation & the initial crossmatch
\author[0000-0002-2792-134X]{J. L. Curtis}
\affiliation{Department of Astronomy, Columbia University, 550 West 120th Street, New York, NY 10027, USA}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY 10024, USA}

% \author[0000-0003-1298-9699]{K. Masuda}
% \affiliation{Department of Earth and Space Science, Osaka University, Osaka 560-0043, Japan}
% 
% % ... planet-fitting, kinematics, meta.
\author{L. A. Hillenbrand}
\affiliation{Cahill Center for Astrophysics, California Institute of Technology, Pasadena, CA 91125, USA}
% 
% % ... RM fitting
% \author[0000-0001-7409-5688]{G. Stefansson}
% \altaffiliation{Henry Norris Russell Fellow}
% \affiliation{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08540, USA}

%
% PFS Collaborators
%
\author[0000-0001-8638-0320]{A. W. Howard}
\affiliation{Cahill Center for Astrophysics, California Institute of Technology, Pasadena, CA 91125, USA}
%
\author[0000-0002-0531-1073]{H. Isaacson}
\affiliation{Astronomy Department, University of California, Berkeley, CA 94720, USA}
% pending

% AO IMAGING
\author[0000-0001-9811-568X]{A.~L.~Kraus}
\affiliation{Department of Astronomy, The University of Texas at Austin, Austin, TX 78712, USA}% % ... Kepler correlations
